Does a fully convective star need a special corona to produce a polar flare?

### 2023-08-08 src/tex/ms.tex
[showyourwork] overleaf sync

\newcommand{\Tcool}{\input{output/T1.tex}}
\newcommand{\Thot}{\input{output/T2.tex}}
\newcommand{\eom}{\input{output/om_flare.tex}}
\newcommand{\eepic}{\input{output/epic_flare.tex}}
\newcommand{\Tqmean}{\input{output/Tqmean.tex}}
\newcommand{\Tfmean}{\input{output/Tfmean.tex}}
\newcommand{\FX}{\input{output/epic_flux.tex}}
\newcommand{\LX}{\input{output/epic_Lx.tex}}
\newcommand{\Lbol}{\input{output/Lbol.tex}}
\newcommand{\ffdalpha}{\input{output/tess_ffd_alpha}}
\newcommand{\ffdbeta}{\input{output/tess_ffd_beta}}
\newcommand{\ffdr}{\input{output/R315}}

@@

\subsection{X-ray luminosity}
\label{sec:discussion:xraylum}
Similar to its temperature make-up, while TIC~277's coronal luminosity relative to bolometric luminosity of $L_X/L_{\rm bol}=\LXLbol$ is somewhat lower than the $L_X/L_{\rm bol}\sim 10^{-3}$ average in the saturated regime~\citep{wright2018stellar}, it is not an outlier to other M dwarfs in this activity regime.

>>>>

\newcommand{\Tcool}{\input{output/T1.tex}}
\newcommand{\Thot}{\input{output/T2.tex}}
\newcommand{\eom}{\input{output/om_flare.tex}}
\newcommand{\eepic}{\input{output/epic_flare.tex}}
\newcommand{\Tqmean}{\input{output/Tqmean.tex}}
\newcommand{\Tfmean}{\input{output/Tfmean.tex}}
\newcommand{\FX}{\input{output/epic_flux.tex}}
\newcommand{\LX}{\input{output/epic_Lx.tex}}
\newcommand{\Lbol}{\input{output/Lbol.tex}}
\newcommand{\LXLbol}{\input{output/lxlbol}}
\newcommand{\ffdalpha}{\input{output/tess_ffd_alpha}}
\newcommand{\ffdbeta}{\input{output/tess_ffd_beta}}
\newcommand{\ffdr}{\input{output/R315}}

@@

\subsection{X-ray luminosity}
\label{sec:discussion:xraylum}
Similar to its temperature make-up, while TIC~277's coronal luminosity relative to bolometric luminosity of $L_X/L_{\rm bol}=$\LXLbol is somewhat lower than the $L_X/L_{\rm bol}\sim 10^{-3}$ average in the saturated regime~\citep{wright2018stellar}, it is not an outlier to other M dwarfs in this activity regime.
